%!TEX root = report.tex
\chapter{Introduction}
\label{sec:introduction}

\section{Dynamic Repricing}
\label{sec:dynamicrepricing}
%% Begin the state (edited)	
Nowadays, the rise of e-commerce has opened many opportunities and challenges 
for merchants to sell their products and re-act their selling immediately. 
The on-line marketplace such as Amazon, provide many supporting tools to sellers 
that they can supervise their products at any given point of time. 
On the one hand, Amazon helps the merchants to adapt their product's 
price effectively in order to gain their profit. On the other hand, it also increases 
much pressures to the retailers, who have limited experience with such highly
competitive markets and their long-term effects. To deal with that concern, the sellers 
use dynamic pricing tools to adjust product prices and manage inventories in real-time. 

%%% What is Dynamic pricing (edited)	
Dynamic repricing, also called dynamic pricing, is an approach to determine an optimal selling price 
for a product or service that is highly flexible. The aim of repricing algorithm is to allow a customer 
to settle their prices effectively to gain their revenue or to achieve a special goal (e.g. win the Amazon BuyBox) in a very competing marketplace. 
Nowadays, dynamic pricing has been used widely in various on-line platforms and in some cases it has considered to be an essential part of pricing policies.

%%% Talk about the key points (edited)	
At the core of a dynamic repricing technique is a machine learning model, which is built from 
the past data of retailer's selling behavior. This data may contain important insights on how the 
seller respond to different selling prices. Exploiting the knowledge contained inside the data and 
applying that to a repricing model may have a competitive advantage. This consideration 
is a main driver of research on dynamic repricing: the study of machine learning model, based on the past behavior of selling data, to find an optimized 
prices for customer's items in order to increase their profit.

\section{Dynamic Product Repricing on the Amazon Marketplace}
\label{sec:intoAMZ}
%% What is our contribution
The Amazon is the largest and fastest growing 
retailer marketplace, with more than 80 million worldwide members in 2017 selling products on this platform (refered to \textit{"Global Powers of Retailing 2017"} report{\footnote{\url{https://www2.deloitte.com/
			content/dam/Deloitte/global/Documents/consumer-industrial-products/gx-cip-2017-global-powers-of-retailing.pdf}}).
Amazon constantly ranks the sellers based on different attributes, 
such as product price, customer satisfaction, amount of transactions completed, etc., and presents the best ranked seller/offer in the BuyBox. 
Pricing is the the most influential factor short-term to rank at the top, but the other attributes describing the seller and the offer are also important (e.g., shipping time, 
stock available).
Existing repricing solutions use seller-provided rules for updating the product price when a repricing event is triggered 
(e.g., update price by 1\% when a competitor changes the price of a product). 
These fixed rules are set manually and changed infrequently based on a schedule decided by the seller.

A Machine Learning solution for dynamic repricing can take full advantage of past 
detailed historical data about competing offers and the outcome of auctions, and should remove the need 
for slow to update and potentially non-optimal manual-rules.
This can result in optimised pricing decisions for the sellers which should rank them top 
on the sales platform consistently, therefore laying the foundation for increased sales and better competitiveness.
%to existing customers and a strengthened value proposition to attract new customers.
Additionally, the insights derived from analysing the historical data and the resulting predictive models should allow sellers 
to adapt to ever changing market conditions beyond pricing. 
%This will result in a deep understanding of parameters, which may result in introducing new parameters or adapting multiple parameters to gain the best result for the customers. 
%This may also lead to additional consulting opportunities for XSellco.
%Solution / Product
%Briefly describe what the team hope to produce from the partnership.
%This project aims to develop scalable Machine Learning methods that can automatically recommend appropriate product repricing, by taking into account historical and dynamic data describing the retailer, the product, the competitor products, demand, etc. A learning approach is needed to automatically infer patterns from dynamic and vast historical data, without the need for human-built rules that do not make the best use of the data available.
%The learning model aims to be accurate and scalable, to be able to deal with millions of repricing events which are constantly changing. The predictive model also aims to be interpretable, so the insights learned from the model can be used by XSellco to offer additional consulting.
%To start with, the project has historical data available from XSellco about thousands of retailers and products, as well as repricing event details from 2013 to today. This data will be used to build predictive models that describe the relationship between data and desired outcomes, such as winning the Amazon ?Buy Box? at the price that maximises profit for the retailer.

In this work we have access to large amounts of auction data 
for products sold over the course of 9 months on the Amazon Marketplace. 
Our aim is to develop machine learning algorithms to predict the BuyBox winner, as well as study  
dynamic repricing strategies for individual sellers.

Our key contributions are as follows:
\begin{itemize}
\item \textbf{Data Preparation Techniques:} We present data pre-processing and preparation techniques suitable for product auction data collected from the Amazon Marketplace, with a view to 
build effective BuyBox prediction algorithms. 
\item	\textbf{BuyBox Predictor Algorithm:} We propose a machine learning algorithm that can be trained on historical product auction data from the Amazon Marketplace, 
and can be used to predict the winner of a new auction on the Amazon Marketplace (i.e., BuyBox winner predictor). 
Our algorithm is based on a RandomForest classifier that uses carefully engineered features.
We also discuss the importance of different features for predicting the BuyBox.

\item \textbf{Repricer Algorithm:} We implement and evaluate a dynamic repricing algorithm that can take in an auction for a given product and seller, 
and recommend a repricing strategy to maximise the probability of winning the next auction for that seller and product.
Our algorithm is based on the BuyBox predictor model and on a strategy for selecting candidate price points for recommendation.

\item \textbf{Evaluation/Deployment:} All our algorithms are tested on research benchmarks and are deployed on commercial platforms.
We discuss the results and what we learn from deploying our algorithms.
\end{itemize}

%-------------------------------------------------------------------------